Towards Cloud Bursting for Extreme Scale Supercomputers\\ (Unrefereed Workshop Manuscript)

### 2014-06-30 paper/src/3_burst_buffer.tex
Changed directory stractures
several updates
Updated 3_burst_buffer

\section{I/O Bursting Buffer Overview}

@@

An overview of I/O burst buffer architecture and two kinds of connection: direct connection and I/O bursting buffer are described in this section.
As we mentioned in the previous section, our model takes advantage of high throughput inside a system, and use buffer queue system in order to increase throughput between two systems.
The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, I/O data will first be buffered in buffer queue in the same system, and then be transferred to final storage system.
%the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in I/O buffer nodes.
%Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
%Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment, also because only a few public IP address available in each cloud, I/O buffer nodes are required even in direct connection model.

@@

\subsection{System Environment}
First a general system used in following sections is defined as follow:

%For security consideration and the fact that IPv4 addresses becomes rare,
\begin{itemize}
	\item All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each system, so topology is not specified here, interconnection network performance is measured by throughput.
	\item There are a constant number of public IP addresses can be assigned to some computing nodes.
	\item There is a shared storage for date sharing inside system, all computing nodes are connected with shared storage, also the filesystem of shared storage is not specified and performance is measured by throughput.
\end{itemize}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[width=6cm]{IOserver}
	\caption{I/O server and buffer queue}
	\label{I/O server}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics[width=6cm]{overview}
	\caption{overall illustrate of I/O Burst Buffer Architecture}
	\label{overview}
\end{figure}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[width=6cm]{read_and_write}
	\caption{read and write operation}
	\label{read and write}
\end{figure}

>>>>

\section{I/O Bursting Buffer Overview}
% Why I/O server in client nodes
\label{sec:burst_buffer}

@@

An overview of I/O burst buffer architecture and two kinds of connection: direct connection and I/O bursting buffer are described in this section.
As we mentioned in the previous section, our model takes advantage of high throughput inside a system, and use buffer queue system in order to increase throughput between two systems.
The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, I/O data will first be buffered in buffer queue in the same system, and then be transferred to final storage system
\kento{how about read ?}.
%the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in I/O buffer nodes.
%Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
%Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment, also because only a few public IP address available in each cloud, I/O buffer nodes are required even in direct connection model.

@@

\subsection{Assumptions}
First, we make several assumptions for the federated environments as follows.
%For security consideration and the fact that IPv4 addresses becomes rare,
\begin{itemize}
	\item All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each system, so topology is not specified here, interconnection network performance is measured by throughput.
	\item There are a constant number of public IP addresses can be assigned to some computing nodes.
	\item There is a shared storage for date sharing inside system, all computing nodes are connected with shared storage, also the filesystem of shared storage is not specified and performance is measured by throughput.
\end{itemize}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[width=6cm]{../img/IOserver}
	\caption{I/O server and buffer queue}
	\label{I/O server}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics[width=6cm]{../img/overview}
	\caption{overall illustrate of I/O Burst Buffer Architecture}
	\label{overview}
\end{figure}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[width=6cm]{../img/read_and_write}
	\caption{read and write operation}
	\label{read and write}
\end{figure}
